Approximation as Differentiation: Notes

### 2025-05-16 notes/cmon-enriched.tex
Roll out PSh_V notation.

\noindent Now suppose $\mathscr{V}$ is monoidal closed. Then the hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op
\to \mathscr{V}$ is itself $\mathscr{V}$-enriched, providing a family of morphisms $\Hom{\cat{C}}{-}{X}_{Y,Z}:
\Hom{\cat{C}}{Y}{Z} \to \Hom{\mathscr{V}}{\Hom{\cat{C}}{Z}{X}}{\Hom{\cat{C}}{Y}{X}}$ in $\mathscr{V}$ for any
$Y, Z$ in $\cat{C}$. Moreover there exists an enriched Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: \cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ which is itself
$\mathscr{V}$-enriched, sending objects $X$ to the $\mathscr{V}$-enriched hom-functor $\Hom{\cat{C}}{-}{X}$
and providing a family of morphisms $(\Yoneda_{\mathscr{V}})_{X,Y}: \Hom{\cat{C}}{X}{Y} \to $ to
$\mathscr{V}$-natural transformations $\Hom{\cat{C}}{-}{X} \naturalto \Hom{\cat{C}}{-}{Y}$ acting at each
component as post-composition with $f$.

@@

\begin{lemma}
Suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed. For any $F: \cat{C}^\op \to
\mathscr{V}$ and any object $X$ in $\cat{C}$:
\[\Hom{\Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}}{\Hom{\cat{C}}{-}{X}}{F} \iso F(X)\]
\end{lemma}

>>>>

\noindent Now suppose $\mathscr{V}$ is monoidal closed. Then the hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op
\to \mathscr{V}$ is itself $\mathscr{V}$-enriched, providing a family of morphisms $\Hom{\cat{C}}{-}{X}_{Y,Z}:
\Hom{\cat{C}}{Y}{Z} \to \Hom{\mathscr{V}}{\Hom{\cat{C}}{Z}{X}}{\Hom{\cat{C}}{Y}{X}}$ in $\mathscr{V}$ for any
$Y, Z$ in $\cat{C}$. Moreover there exists an enriched Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: \cat{C} \to \PSh_{\mathscr{V}}(\cat{C})$ which is itself $\mathscr{V}$-enriched,
sending objects $X$ to the $\mathscr{V}$-enriched hom-functor $\Hom{\cat{C}}{-}{X}$ and providing a family of
morphisms $(\Yoneda_{\mathscr{V}})_{X,Y}: \Hom{\cat{C}}{X}{Y} \to
\Hom{\PSh_{\mathscr{V}}(\cat{C})}{\Hom{\cat{C}}{-}{X}}{\Hom{\cat{C}}{-}{Y}}$ acting concretely at each
component as post-composition with $f: X \to Y$.

The $\CMon$-enriched Yoneda embedding preserves biproducts:

\begin{proposition}
\end{proposition}

@@

\begin{lemma}
Suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed. For any $F: \cat{C}^\op \to
\mathscr{V}$ and any object $X$ in $\cat{C}$:
\[\Hom{\PSh_{\mathscr{V}}{(\cat{C})}}{\Hom{\cat{C}}{-}{X}}{F} \iso F(X)\]
\end{lemma}
